Classical Mechanics Assignment One

### 2015-10-05 classical/latex/a1.tex

>>>>

\section{Problem One}
\textbf{What do you expect from this course?} \\ \\
       {From this course I want to learn the physics techniques for modeling more complicated systems than what was taught in the introductory physics sequence. I want to get a better understanding for how physical modeling works and get a better intution for when to use particular techniques to model physical systems. I'd also like to learn how to use advanced techniques, like the Lagrangian, to characterizing physical systems.}

\vspace{1 cm}

\section{Problem Two}
\textbf{What do you expect from the instructor?} \\ \\
       {I expect the professor to answer questions during lecture and be available for office hours for help and clarification on homework assignments.}

\vspace{1 cm}

\section{Problem Three}
\textbf{What do you expect from your classmates?} \\ \\
       {I expect my classmates to not be disruptive during lecture and work to create an environment conducive to learning. I expect them not to ask for homework solutions, but to ask for help on homework when needed.}

\vspace{1 cm}

\section{Problem Four}
\textbf{How prepared do you feel that you are for this class?} \\ \\
       {I feel adequately prepared. I have taken the Paradigms series in the past year, in addition to the two linear algebra courses and calculus series recommended for this course. I am not worried about the material, and know that if anything challenging comes up, I can always do research, ask my classmates or the professor for help.}
